Changing face of pediatric pulmonary exacerbations in CF

### 2023-03-29 Scott Sagel/PEx in CF/nacfc_2023.qmd
Update nacfc_2023.qmd

---
title: "Changing face of pediatric pulmonary exacerbations in CF"
author: "Tim Vigers"
date: "today"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
execute: 
  echo: false
---

@@

@@

1. For each person with multiple admissions, continuous variables were averaged prior to generating summary tables.
2. If a participant was on a modulators during any admission, they were counted as on modulators for that year. For example, participant 4 from CHOC was hospitalized 3 times in 2018 and was on a modulator during one of those admissions, so they were counted as on modulators in 2018.
3. CNH only included combined P. aeruginosa information.

@@

```{r}
#| label: tbl-chco
#| tbl-cap: Summary by Year
#| message: false
summ %>%
  select(-`Unique number`,-Site) %>%
  tbl_summary(by=Year,
              type = list(`# of Hospitalizations per Person` ~ 'continuous'),
              statistic = list(
                c("# of Hospitalizations per Person","# Days in Admit") ~ "{median} ({p25}, {p75})",
                c("Age at Admit","Change in FEV1","FEV1 % Predicted at Admit",
                  "FEV1 % Predicted at Discharge") ~ "{mean} ({sd})"
              ),
              missing_text = "(Missing)") %>%
  add_ci(pattern = "{stat} [{ci}]") %>%
  add_p(test = list(
    `Age at Admit`~"t.test",
    `Change in FEV1`~"t.test"
  )) %>%
  separate_p_footnotes() %>%
  as_gt()
```

The number of hospitalizations for PEx decreased from `r sum(summ$Year==2018)` in 2018 to `r sum(summ$Year==2022)` in 2022.

>>>>

---
title: "Changing face of pediatric pulmonary exacerbations in CF"
author: "Tim Vigers"
date: "today"
format:
  html:
    toc: false
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
execute: 
  echo: false
---

@@

library(gt)

@@

1. For each person with multiple admissions, continuous variables were averaged prior to generating summary tables.
2. If a participant was on a modulators during any admission, they were counted as on modulators for that year. For example, participant 4 from CHOC was hospitalized 3 times in 2018 and was on a modulator during one of those admissions, so they were counted as on modulators in 2018.
3. CNH only included combined P. aeruginosa information.
4. Participants were uniquely identified by ID, site, and year.

The number of hospitalizations for PEx decreased from `r sum(df$Year==2018)` in 2018 to `r sum(df$Year==2022)` in 2022.

@@

```{r}
#| label: tbl-all
#| tbl-cap: Summary by Year
#| message: false
summ %>%
  select(-`Unique number`,-Site) %>%
  tbl_summary(by=Year,
              type = list(`# of Hospitalizations per Person` ~ 'continuous'),
              statistic = list(
                c("# of Hospitalizations per Person","# Days in Admit") ~ "{median} ({p25}, {p75})",
                c("Age at Admit","Change in FEV1","FEV1 % Predicted at Admit",
                  "FEV1 % Predicted at Discharge") ~ "{mean} ({sd})"
              ),
              missing_text = "(Missing)") %>%
  add_ci(pattern = "{stat} [{ci}]") %>%
  add_p(test = list(
    `Age at Admit`~"t.test",
    `Change in FEV1`~"t.test"
  )) %>%
  separate_p_footnotes() %>%
  as_gt() %>%
  as_raw_html()
```

```{r}
#| label: tbl-site
#| tbl-cap: Stratified by Site
#| message: false
summ %>%
  select(-`Unique number`) %>%
  tbl_strata(
    strata = Site,
    .tbl_fun =
      ~ .x %>%
      tbl_summary(by=Year,
              type = list(`# of Hospitalizations per Person` ~ 'continuous'),
              statistic = list(
                c("# of Hospitalizations per Person","# Days in Admit") ~ "{median} ({p25}, {p75})",
                c("Age at Admit","Change in FEV1","FEV1 % Predicted at Admit",
                  "FEV1 % Predicted at Discharge") ~ "{mean} ({sd})"
              ),
              missing_text = "(Missing)") %>%
  add_ci(pattern = "{stat} [{ci}]") %>%
  add_p(test = list(
    `Age at Admit`~"t.test",
    `Change in FEV1`~"t.test"
  )) %>%
  separate_p_footnotes()
  ) %>%
  as_gt() %>%
  as_raw_html()
```
